Data Preparation, Integration and Cleaning

### 2018-04-05 abbDataPrep_Script.Rmd
Updates: Data load in prep

  data.path <- 'c:/dropbox/research/airBNB/data/'
  code.path <- 'c:/code/'
  fig.path <- 'c:/dropbox/research/airBNB/figures/'

@@

  source(paste0(code.path, "research/AirBNBMelbourne/abb_Functions.R"))

@@

  source(paste0(code.path, 'tools/dataVizTools/ggPlotTools.R'))
  source(paste0(code.path, 'tools/datamgmttools/dataMungeTools.R'))
  source(paste0(code.path, 'tools/spatialTools/spatialLogitModels.R'))
  source(paste0(code.path, 'tools/spatialTools/point2surface_Tools.R'))

@@

@@

  abb.colors.names=c('rausch', 'hackberry', 'kazan', 'babu', 'lima', 'beach',
                     'ebisu', 'tirol', 'foggy', 'hof')
  abb.col <- c(rgb(250,88,99, maxColorValue=255), rgb(139,14,82, maxColorValue=255),
               rgb(0,117,140, maxColorValue=255), rgb(4,211,191, maxColorValue=255), 
               rgb(77,226,110, maxColorValue=255), rgb(252,179,14, maxColorValue=255),
               rgb(249,177,139, maxColorValue=255), rgb(191,166,100, maxColorValue=255),
               rgb(156,161,155, maxColorValue=255), rgb(86,94,97, maxColorValue=255))

@@

  str.col <- abb.col[1]
  ltr.col <- abb.col[3]

@@

  load(paste0(data.path, 'prepared/stpropdata.RData'))

@@

  load(paste0(data.path, 'prepared/stdailydata.RData'))

@@

  load(paste0(data.path, 'prepared/ltpropdata.RData'))

@@

  load(paste0(data.path, 'prepared/ltlistdata.RData'))

@@

  suburbs.shp <- readShapePoly(paste0(data.path, 'geographic/melbSuburbs.shp'),
                               proj4string=CRS("+init=epsg:4283"),
                               delete_null_obj=TRUE)
  names(suburbs.shp@data) <- tolower(names(suburbs.shp@data))

@@

  sa1s.shp <- readShapePoly(paste0(data.path, 'geographic/sa1s.shp'),
                            proj4string=CRS("+init=epsg:4283"),
                            delete_null_obj=TRUE)
  names(sa1s.shp@data) <- tolower(names(sa1s.shp@data))

@@

  beach.shp <- readShapePoly(paste0(data.path, 'geographic/portPhillipBeach.shp'),
                             proj4string=CRS("+init=epsg:4283"),
                             delete_null_obj=TRUE)
  names(beach.shp@data) <- tolower(names(beach.shp@data))

@@

  ltr.data <- ltr.data[ ,ltr.keep.flds]

@@

  names(ltr.data) <- c('id.key', 'geographical.id', 
                        'event.id', 'address.id', 'activity.id',
                        'flat.number', 'street.number', 'street.name', 'street.type',
                        'suburb', 'postcode', 'latitude', 'longitude',
                        'street.latitude', 'street.longitude', 'event.date',
                        'event.price', 'property.type', 'area.size', 'bedrooms',
                        'baths', 'parking', 'has.study', 'has.courtyard',
                        'has.balcony', 'has.aircond', 'has.garage', 'dom')

@@

  ltr.data <- ltr.data[ltr.data$event.date >= (strike_date - 365) & 
                            ltr.data$event.date <= (strike_date - 1), ]
  listing.data <- listing.data[listing.data$id.key %in% ltr.data$id.key, ]

@@

  ltr.data$ltr.month <- as.numeric(as.factor(substr(ltr.data$event.date, 1, 7)))
  listing.data$ltr.month <- as.numeric(as.factor(substr(
    listing.data$event.date, 1, 7))) - 8

@@

  ltr.data$type <- 'Other'
  ltr.data$type[ltr.data$property.type %in% c('Duplex', 'House',
                                           'Terrace', 'Townhouse')] <- 'House'
  ltr.data$type[ltr.data$property.type %in% c('Studio', 'Unit')] <- 'Apartment'

@@

  str.types <- ggplot(str_df, aes(x=type)) + 
    geom_bar(color=str.col, fill=str.col) +
    xlab('\nProperty Type\n') + 
    ggtitle('\nShort Term Rentals\n')  +
    ylab('# of Properties\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr.types <- ggplot(ltr.data, aes(x=type)) + 
    geom_bar(color=ltr.col, fill=ltr.col) +
    xlab('\nProperty Type\n') + 
    ggtitle('\nLong Term Rentals\n')  +
    ylab('# of Properties\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  str_df <- subset(str_df, type != 'Other')
  ltr.data <- subset(ltr.data, type != 'Other')

@@

  list.types <- ggplot(str_df, aes(x=listing.type)) + 
      geom_bar(color=str.col, fill=str.col) +
      xlab('\nListing Type\n') + 
      ggtitle('\nShort Term Rentals by Listing Type\n')  +
      ylab('# of Properties\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr.data$has.study <- ifelse(ltr.data$has.study == 'True', 1, 0)
  ltr.data$has.courtyard <- ifelse(ltr.data$has.courtyard == 'True', 1, 0)
  ltr.data$has.aircon <- ifelse(ltr.data$has.aircon == 'True', 1, 0)
  ltr.data$has.balcony <- ifelse(ltr.data$has.balcony == 'True', 1, 0)
  ltr.data$has.garage <- ifelse(ltr.data$has.garage == 'True', 1, 0)

@@

  # Long term data
  ltr.data <- ltr.data[!is.na(ltr.data$bedrooms), ]
  ltr.data <- ltr.data[ltr.data$bedrooms <= 10, ]

@@

   ltrbed <- ggplot(ltr.data, aes(x=bedrooms)) + 
    geom_bar(fill=ltr.col, color=ltr.col) +
    facet_wrap(~type,scales='free_y') +
    scale_x_continuous(labels=1:10, breaks=1:10)+
    xlab('\nBedrooms\n') +
    scale_y_continuous(labels=c(0,10000,20000), 
                       breaks=c(0,10000,20000))+
    ylab('') +
    ggtitle('Bedrooms in Long Term Rentals') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  strbed <- ggplot(str_df, aes(x=bedrooms)) + 
    geom_bar(fill=str.col, color=str.col) +
    facet_wrap(~type,scales='free_y') +
    scale_x_continuous(labels=0:10, breaks=0:10) +
    xlab('\nBedrooms\n') +
    ylab('') +
    ggtitle('Bedrooms in Short Term Rentals') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  str_df <- str_df[str_df$bedrooms < 5, ]
  ltr.data <- ltr.data[ltr.data$bedrooms < 5, ]

@@

  str.id <- which(str_df$bedrooms > 3 & str_df$type =='Apartment')
  ltr.id <- which(ltr.data$bedrooms > 3 & ltr.data$type =='Apartment')

  if(length(str.id) > 0) str_df <- str_df[-str.id, ]
  if(length(ltr.id) > 0) ltr.data <- ltr.data[-ltr.id, ]

@@

  ltr.data <- ltr.data[!is.na(ltr.data$baths), ]
  str_df <- str_df[!is.na(str_df$baths), ]

@@

  ltbath <- ggplot(ltr.data, aes(x=baths)) + 
    geom_bar(fill=ltr.col, color=ltr.col) +
    facet_wrap(~type) +
    scale_x_continuous(labels=1:8, breaks=1:8)+
    xlab('\nBathrooms\n') +
    ylab('') + 
    ggtitle('Bathrooms in Long Term Rentals') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  stbath <- ggplot(str_df, aes(x=baths)) + 
    geom_bar(fill=str.col, color=str.col) +
    facet_wrap(~type, scales='free_y') +
    scale_x_continuous(labels=0:8, breaks=0:8)+
    xlab('\nBathrooms\n') +
    ylab('') + 
    ggtitle('Bathrooms in Short Term ltrals') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  # Long term data
  ltr.data <- ltr.data[ltr.data$baths < 4, ]

@@

  ltr.data$bedbath <- paste0(ltr.data$bedrooms, '..', ltr.data$baths)
  str_df$bedbath <- paste0(str_df$bedrooms, '..', str_df$baths)

@@

  ltbb <- ggplot(ltr.data, aes(x=bedbath)) + 
    geom_bar(fill=ltr.col, color=ltr.col) +
    xlab('\nBed/Bath Combo\n') +
    ylab('Number of Properties\n') +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    ggtitle('Long Term Rentals') + 
    facet_wrap(~type, scales='free_y')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  stbb <- ggplot(str_df, aes(x=bedbath)) +
    geom_bar(fill=str.col, color=str.col) + 
    xlab('\nBed/Bath Combo\n') +
    ylab('Number of Properties\n') +
    ggtitle('Short Term Rentals') + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    facet_wrap(~type, scales='free_y')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr.data <- ltr.data[ltr.data$bedbath %in% acc.bb, ]
  str_df <- str_df[str_df$bedbath %in% acc.bb, ]

@@

  str_df$bedbath <- factor(str_df$bedbath, 
                              levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
  ltr.data$bedbath <- factor(ltr.data$bedbath, 
                               levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))

@@

  str_df$product <- paste0(substr(str_df$type, 1, 1), str_df$bedbath)
  ltr.data$product <- paste0(substr(ltr.data$type, 1, 1), ltr.data$bedbath)

@@

  ltr.data <- ltr.data[!is.na(ltr.data$event.price), ]
  str_df <- str_df[!is.na(str_df$nightly.rate), ]

@@

  ltr.plot <- ggplot(ltr.data, aes(x=event.price)) + 
    geom_density(fill=ltr.col, alpha=.8) +
    ylab('') +
    xlab('Weekly Rental') + 
    ggtitle('Long Term Rentals') + 
    scale_x_continuous(limits=c(0, 1500)) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank()) +
    theme(plot.title = element_text(hjust = 0.5))

  # Nightly Rate plot
  rate.plot <- ggplot(str_df, aes(x=nightly.rate)) + 
    geom_density(fill=str.col, alpha=.8) + 
    ylab('') +
    xlab('Nightly Rate') +
    ggtitle('Short Term Rentals') + 
    scale_x_continuous(limits=c(0, 600)) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank()) +
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr.data <- ltr.data[ltr.data$event.price >= 200 & 
                         ltr.data$event.price <= 1000, ]

@@

  str_df$gross.revenue <- (str_df$bookings * str_df$med.rate) 
  ltr.data$gross.revenue <- ltr.data$event.price * (52 - ltr.data$dom / 7)

  str.small <- str_df[,c('baths', 'gross.revenue')]
  str.small$tenure <- 'short-term'
  ltr.small <- ltr.data[,c('baths', 'gross.revenue')]
  ltr.small$tenure <- 'long-term'
  all.small <- rbind(str.small, ltr.small)

  revdens <- ggplot(all.small, aes(x=gross.revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=c(ltr.col, abb.col)) +
    scale_color_manual(values=c(ltr.col, abb.col)) +
    ggtitle('Annual Revenues by Tenure Type') +
    xlab('Annual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
    theme(legend.position='bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000))

@@

  ltr.data <- ltr.data[ltr.data$dom <= 180, ]

@@

  # Limit to extent of data
  sub.table <- table(ltr.data$suburb)
  sub.table <- sub.table[sub.table != 0]

@@

  # Set colors
  g.cols <- c('grey10', 'grey40', 'grey70')

  # Make map
  loc.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
    scale_fill_manual(values=g.cols, labels=c('Inner      ',
                                              'Middle      ',
                                              'Outer')) +
    geom_path(data=subs[subs$des=='Outer', ], 
              aes(x=long, y=lat, group=group), col='white', size=.1,
              linetype=1) +

@@

  miss.LL <- which(is.na(ltr.data$latitude))

@@

  ltr.data$miss.LL <- 0
  ltr.data$miss.LL[miss.LL] <- 1

@@

  ltr.data$latitude[miss.LL] <- ltr.data$street.latitude[miss.LL]
  ltr.data$longitude[miss.LL] <- ltr.data$street.longitude[miss.LL]

@@

  ltr.data <- ltr.data[!is.na(ltr.data$latitude), ]

@@

  ltr.prop.shp <- SpatialPointsDataFrame(cbind(ltr.data$longitude,
                                               ltr.data$latitude),
                                         ltr.data,
                                         proj4string=CRS("+init=epsg:4283"))

@@

  spJoin <- over(ltr.prop.shp, suburbs.shp)
  ltr.data$suburb <- as.character(spJoin$name_2006)
  ltr.data$suburb[is.na(ltr.data$suburb)] <- 'missing'

@@

  ltr.data$sub.class <- as.character(spJoin$suburbdesi)
  ltr.data$sub.class[is.na(ltr.data$sub.class)] <- 'missing'

@@

  spJoin <- over(ltr.prop.shp, sa1s.shp)
  ltr.data$sa1 <- spJoin$sa1_main11

@@

  spJoin <- over(ltr.prop.shp, beach.buffer)
  ltr.data$beach <- ifelse(is.na(spJoin), 0 ,1)

@@

  ltr.data <- ltr.data[ltr.data$sub.class != 'missing', ]
  ltr.data <- ltr.data[ltr.data$sa1 != 'missing', ]

@@

  # Add individual classes
  ltr.data$geo.mrkt <- 'rural'
  ltr.data$geo.mrkt[ltr.data$sub.class == 'Middle'] <- 'suburban'
  ltr.data$geo.mrkt[ltr.data$sub.class == 'Inner'] <- 'city'
  ltr.data$geo.mrkt[ltr.data$suburb %in% core.suburbs] <- 'city-core'
  ltr.data$geo.mrkt[ltr.data$beach == 1] <- 'beach'

  # Order the factors properly
  ltr.data$geo.mrkt <- factor(ltr.data$geo.mrkt, 
                              levels=c('city-core', 'city', 'suburban', 
                                        'rural', 'beach'))

@@

  sm.col <- abb.col[c(1, 3, 6, 5, 2)]

@@

  str.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
    geom_point(data=str_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.2,
               alpha=.2) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) + 
    ggtitle('Short-Term Rental Locations')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
    geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=geo.mrkt), size=.1,
               alpha=.1) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) + 
    ggtitle('Long-Term Rental Locations')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  # Convert suburbs from factor to character
  str_df$suburb <- as.character(str_df$suburb)
  ltr.data$suburb <- as.character(ltr.data$suburb)

>>>>

  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
  code_path <- file.path('c:', 'code')
  fig_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'figures')

@@

  source(file.path(getwd(), 'functions', 'abb_Functions.R'))

@@

    source(file.path(code_path, 'tools', 'dataVizTools', 'ggPlotTools.R'))
    source(file.path(code_path, 'tools', 'datamgmttools', 'dataMungeTools.R'))
    source(file.path(code_path, 'tools', 'spatialTools', 'spatialLogitModels.R'))
    source(file.path(code_path, 'tools', 'spatialTools', 'point2surface_Tools.R'))

@@

### HERE

@@

  abb_colors.names=c('rausch', 'hackberry', 'kazan', 'babu', 'lima', 'beach',
                     'ebisu', 'tirol', 'foggy', 'hof')
  abb_col <- c(rgb(250,88,99, maxColorValue=255), rgb(139,14,82, maxColorValue=255),
               rgb(0,117,140, maxColorValue=255), rgb(4,211,191, maxColorValue=255), 
               rgb(77,226,110, maxColorValue=255), rgb(252,179,14, maxColorValue=255),
               rgb(249,177,139, maxColorValue=255), rgb(191,166,100, maxColorValue=255),
               rgb(156,161,155, maxColorValue=255), rgb(86,94,97, maxColorValue=255))

@@

  str_col <- abb_col[1]
  ltr_col <- abb_col[3]

@@

  str_df <- readRDS(file.path(data_path, 'prepared', 'st_prop.RDS'))

@@

  daily_df <- readRDS(file.path(data_path, 'prepared', 'st_daily.RDS'))

@@

  ltr_df <- readRDS(file.path(data_path, 'prepared', 'lt_prop.RDS'))

@@

  list_df <- readRDS(file.path(data_path, 'prepared', 'lt_list.RDS'))

@@

  suburbs_shp <- readShapePoly(file.path(data_path, 'geographic', 'melbSuburbs.shp'),
                               proj4string=CRS("+init=epsg:4283"),
                               delete_null_obj=TRUE)
  names(suburbs_shp@data) <- tolower(names(suburbs_shp@data))

@@

  sa1s_shp <- readShapePoly(file.path(data_path, 'geographic', 'sa1s.shp'),
                            proj4string=CRS("+init=epsg:4283"),
                            delete_null_obj=TRUE)
  names(sa1s_shp@data) <- tolower(names(sa1s_shp@data))

@@

  beach_shp <- readShapePoly(file.path(data_path, 'geographic','portPhillipBeach.shp'),
                             proj4string=CRS("+init=epsg:4283"),
                             delete_null_obj=TRUE)
  names(beach_shp@data) <- tolower(names(beach_shp@data))

@@

  ltr_df <- ltr_df[ ,ltr.keep.flds]

@@

  names(ltr_df) <- c('id.key', 'geographical.id', 
                        'event.id', 'address.id', 'activity.id',
                        'flat.number', 'street.number', 'street.name', 'street.type',
                        'suburb', 'postcode', 'latitude', 'longitude',
                        'street.latitude', 'street.longitude', 'event.date',
                        'event.price', 'property.type', 'area.size', 'bedrooms',
                        'baths', 'parking', 'has.study', 'has.courtyard',
                        'has.balcony', 'has.aircond', 'has.garage', 'dom')

@@

  ltr_df <- ltr_df[ltr_df$event.date >= (strike_date - 365) & 
                            ltr_df$event.date <= (strike_date - 1), ]
  listing.data <- listing.data[listing.data$id.key %in% ltr_df$id.key, ]

@@

  ltr_df$ltr.month <- as.numeric(as.factor(substr(ltr_df$event.date, 1, 7)))
  listing.data$ltr.month <- as.numeric(as.factor(substr(
    listing.data$event.date, 1, 7))) - 8

@@

  ltr_df$type <- 'Other'
  ltr_df$type[ltr_df$property.type %in% c('Duplex', 'House',
                                           'Terrace', 'Townhouse')] <- 'House'
  ltr_df$type[ltr_df$property.type %in% c('Studio', 'Unit')] <- 'Apartment'

@@

  str.types <- ggplot(str_df, aes(x=type)) + 
    geom_bar(color=str_col, fill=str_col) +
    xlab('\nProperty Type\n') + 
    ggtitle('\nShort Term Rentals\n')  +
    ylab('# of Properties\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr.types <- ggplot(ltr_df, aes(x=type)) + 
    geom_bar(color=ltr_col, fill=ltr_col) +
    xlab('\nProperty Type\n') + 
    ggtitle('\nLong Term Rentals\n')  +
    ylab('# of Properties\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  str_df <- subset(str_df, type != 'Other')
  ltr_df <- subset(ltr_df, type != 'Other')

@@

  list.types <- ggplot(str_df, aes(x=listing.type)) + 
      geom_bar(color=str_col, fill=str_col) +
      xlab('\nListing Type\n') + 
      ggtitle('\nShort Term Rentals by Listing Type\n')  +
      ylab('# of Properties\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr_df$has.study <- ifelse(ltr_df$has.study == 'True', 1, 0)
  ltr_df$has.courtyard <- ifelse(ltr_df$has.courtyard == 'True', 1, 0)
  ltr_df$has.aircon <- ifelse(ltr_df$has.aircon == 'True', 1, 0)
  ltr_df$has.balcony <- ifelse(ltr_df$has.balcony == 'True', 1, 0)
  ltr_df$has.garage <- ifelse(ltr_df$has.garage == 'True', 1, 0)

@@

  # Long term data
  ltr_df <- ltr_df[!is.na(ltr_df$bedrooms), ]
  ltr_df <- ltr_df[ltr_df$bedrooms <= 10, ]

@@

   ltrbed <- ggplot(ltr_df, aes(x=bedrooms)) + 
    geom_bar(fill=ltr_col, color=ltr_col) +
    facet_wrap(~type,scales='free_y') +
    scale_x_continuous(labels=1:10, breaks=1:10)+
    xlab('\nBedrooms\n') +
    scale_y_continuous(labels=c(0,10000,20000), 
                       breaks=c(0,10000,20000))+
    ylab('') +
    ggtitle('Bedrooms in Long Term Rentals') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  strbed <- ggplot(str_df, aes(x=bedrooms)) + 
    geom_bar(fill=str_col, color=str_col) +
    facet_wrap(~type,scales='free_y') +
    scale_x_continuous(labels=0:10, breaks=0:10) +
    xlab('\nBedrooms\n') +
    ylab('') +
    ggtitle('Bedrooms in Short Term Rentals') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  str_df <- str_df[str_df$bedrooms < 5, ]
  ltr_df <- ltr_df[ltr_df$bedrooms < 5, ]

@@

  str.id <- which(str_df$bedrooms > 3 & str_df$type =='Apartment')
  ltr.id <- which(ltr_df$bedrooms > 3 & ltr_df$type =='Apartment')

  if(length(str.id) > 0) str_df <- str_df[-str.id, ]
  if(length(ltr.id) > 0) ltr_df <- ltr_df[-ltr.id, ]

@@

  ltr_df <- ltr_df[!is.na(ltr_df$baths), ]
  str_df <- str_df[!is.na(str_df$baths), ]

@@

  ltbath <- ggplot(ltr_df, aes(x=baths)) + 
    geom_bar(fill=ltr_col, color=ltr_col) +
    facet_wrap(~type) +
    scale_x_continuous(labels=1:8, breaks=1:8)+
    xlab('\nBathrooms\n') +
    ylab('') + 
    ggtitle('Bathrooms in Long Term Rentals') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  stbath <- ggplot(str_df, aes(x=baths)) + 
    geom_bar(fill=str_col, color=str_col) +
    facet_wrap(~type, scales='free_y') +
    scale_x_continuous(labels=0:8, breaks=0:8)+
    xlab('\nBathrooms\n') +
    ylab('') + 
    ggtitle('Bathrooms in Short Term ltrals') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  # Long term data
  ltr_df <- ltr_df[ltr_df$baths < 4, ]

@@

  ltr_df$bedbath <- paste0(ltr_df$bedrooms, '..', ltr_df$baths)
  str_df$bedbath <- paste0(str_df$bedrooms, '..', str_df$baths)

@@

  ltbb <- ggplot(ltr_df, aes(x=bedbath)) + 
    geom_bar(fill=ltr_col, color=ltr_col) +
    xlab('\nBed/Bath Combo\n') +
    ylab('Number of Properties\n') +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    ggtitle('Long Term Rentals') + 
    facet_wrap(~type, scales='free_y')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  stbb <- ggplot(str_df, aes(x=bedbath)) +
    geom_bar(fill=str_col, color=str_col) + 
    xlab('\nBed/Bath Combo\n') +
    ylab('Number of Properties\n') +
    ggtitle('Short Term Rentals') + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    facet_wrap(~type, scales='free_y')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr_df <- ltr_df[ltr_df$bedbath %in% acc.bb, ]
  str_df <- str_df[str_df$bedbath %in% acc.bb, ]

@@

  str_df$bedbath <- factor(str_df$bedbath, 
                              levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))
  ltr_df$bedbath <- factor(ltr_df$bedbath, 
                               levels=c('2..2', '1..1', '2..1', '3..1', '3..2', '4..2'))

@@

  str_df$product <- paste0(substr(str_df$type, 1, 1), str_df$bedbath)
  ltr_df$product <- paste0(substr(ltr_df$type, 1, 1), ltr_df$bedbath)

@@

  ltr_df <- ltr_df[!is.na(ltr_df$event.price), ]
  str_df <- str_df[!is.na(str_df$nightly.rate), ]

@@

  ltr.plot <- ggplot(ltr_df, aes(x=event.price)) + 
    geom_density(fill=ltr_col, alpha=.8) +
    ylab('') +
    xlab('Weekly Rental') + 
    ggtitle('Long Term Rentals') + 
    scale_x_continuous(limits=c(0, 1500)) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank()) +
    theme(plot.title = element_text(hjust = 0.5))

  # Nightly Rate plot
  rate.plot <- ggplot(str_df, aes(x=nightly.rate)) + 
    geom_density(fill=str_col, alpha=.8) + 
    ylab('') +
    xlab('Nightly Rate') +
    ggtitle('Short Term Rentals') + 
    scale_x_continuous(limits=c(0, 600)) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank()) +
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr_df <- ltr_df[ltr_df$event.price >= 200 & 
                         ltr_df$event.price <= 1000, ]

@@

  str_df$gross.revenue <- (str_df$bookings * str_df$med.rate) 
  ltr_df$gross.revenue <- ltr_df$event.price * (52 - ltr_df$dom / 7)

  str.small <- str_df[,c('baths', 'gross.revenue')]
  str.small$tenure <- 'short-term'
  ltr.small <- ltr_df[,c('baths', 'gross.revenue')]
  ltr.small$tenure <- 'long-term'
  all.small <- rbind(str.small, ltr.small)

  revdens <- ggplot(all.small, aes(x=gross.revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=c(ltr_col, abb_col)) +
    scale_color_manual(values=c(ltr_col, abb_col)) +
    ggtitle('Annual Revenues by Tenure Type') +
    xlab('Annual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
    theme(legend.position='bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000))

@@

  ltr_df <- ltr_df[ltr_df$dom <= 180, ]

@@

  # Limit to extent of data
  sub.table <- table(ltr_df$suburb)
  sub.table <- sub.table[sub.table != 0]

@@

  # Set colors
  g_cols <- c('grey10', 'grey40', 'grey70')

  # Make map
  loc.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
    scale_fill_manual(values=g_cols, labels=c('Inner      ',
                                              'Middle      ',
                                              'Outer')) +
    geom_path(data=subs[subs$des=='Outer', ], 
              aes(x=long, y=lat, group=group), col='white', size=.1,
              linetype=1) +

@@

  miss.LL <- which(is.na(ltr_df$latitude))

@@

  ltr_df$miss.LL <- 0
  ltr_df$miss.LL[miss.LL] <- 1

@@

  ltr_df$latitude[miss.LL] <- ltr_df$street.latitude[miss.LL]
  ltr_df$longitude[miss.LL] <- ltr_df$street.longitude[miss.LL]

@@

  ltr_df <- ltr_df[!is.na(ltr_df$latitude), ]

@@

  ltr.prop.shp <- SpatialPointsDataFrame(cbind(ltr_df$longitude,
                                               ltr_df$latitude),
                                         ltr_df,
                                         proj4string=CRS("+init=epsg:4283"))

@@

  spJoin <- over(ltr.prop.shp, suburbs.shp)
  ltr_df$suburb <- as.character(spJoin$name_2006)
  ltr_df$suburb[is.na(ltr_df$suburb)] <- 'missing'

@@

  ltr_df$sub.class <- as.character(spJoin$suburbdesi)
  ltr_df$sub.class[is.na(ltr_df$sub.class)] <- 'missing'

@@

  spJoin <- over(ltr.prop.shp, sa1s.shp)
  ltr_df$sa1 <- spJoin$sa1_main11

@@

  spJoin <- over(ltr.prop.shp, beach.buffer)
  ltr_df$beach <- ifelse(is.na(spJoin), 0 ,1)

@@

  ltr_df <- ltr_df[ltr_df$sub.class != 'missing', ]
  ltr_df <- ltr_df[ltr_df$sa1 != 'missing', ]

@@

  # Add individual classes
  ltr_df$geo.mrkt <- 'rural'
  ltr_df$geo.mrkt[ltr_df$sub.class == 'Middle'] <- 'suburban'
  ltr_df$geo.mrkt[ltr_df$sub.class == 'Inner'] <- 'city'
  ltr_df$geo.mrkt[ltr_df$suburb %in% core.suburbs] <- 'city-core'
  ltr_df$geo.mrkt[ltr_df$beach == 1] <- 'beach'

  # Order the factors properly
  ltr_df$geo.mrkt <- factor(ltr_df$geo.mrkt, 
                              levels=c('city-core', 'city', 'suburban', 
                                        'rural', 'beach'))

@@

  sm_col <- abb_col[c(1, 3, 6, 5, 2)]

@@

  str.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
    geom_point(data=str_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.2,
               alpha=.2) +
    scale_color_manual(values=sm_col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) + 
    ggtitle('Short-Term Rental Locations')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
    geom_point(data=ltr_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.1,
               alpha=.1) +
    scale_color_manual(values=sm_col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) + 
    ggtitle('Long-Term Rental Locations')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  # Convert suburbs from factor to character
  str_df$suburb <- as.character(str_df$suburb)
  ltr_df$suburb <- as.character(ltr_df$suburb)
